---
title: "Fundamental R Operations"
author: "Zichen Men"
output: html_document
---

## Problem 1: Compute the Product of the First Ten Integers
### Manually doing the multiplication of all ten numbers on one line
```{r}
1 * 2 * 3 * 4 * 5 * 6 * 7 * 8 * 9 * 10
```
### Using for loop
```{r}
product <- 1
for (i in 1:10) {
  product <- product * i
}
product
```

### Using inbuilt prod function
```{r}
prod(1:10)
```

### Using inbuilt factorial function
```{r}
factorial(10)
```

## Problem 2: Vectors and Data Frame Operations
### Create two vectors and a data frame

```{r}
height <- c(168, 172, 165, 180, 174)
weight <- c(65, 70, 60, 85, 75)
HWFrame <- data.frame(height, weight)
print(HWFrame)
```
### Mean and variance of height
```{r}
mean_height <- mean(HWFrame$height)
variance_height <- var(HWFrame$height)
```
### Correlation between height and weight
```{r}
correlation <- cor(HWFrame$height, HWFrame$weight)
```

## Problem 3: Phone Usage Analysis
### Data entry and summary statistics
```{r}
minutes <- c(65, 55, 28, 0, 80, 100, 23)
summary(minutes)
```
### Days with more than 50 minutes usage
```{r}
days_over_50 <- sum(minutes >= 50)
percentage_over_50 <- (days_over_50 / length(minutes)) * 100
```

## Problem 4: Generating Random Data and Creating Graphs
### Histogram of normal distribution
```{r}
x <- rnorm(100)
hist(x, main="Histogram of Normal Distribution", xlab="Values")
```

### Boxplot of normal distribution
```{r}
boxplot(x, main="Boxplot of Normal Distribution")
```

### Histogram of Poisson distribution
```{r}
y <- rpois(100, lambda = 18)
hist(y, main="Histogram of Poisson Distribution", xlab="Values")
```
